---
title: "GSS challenge"
author: "Cyann  Arevalo"
date: "October 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?
  
$H_O$ The Null Hypothesis is that there is no relationship between belief in the BIGBANG theory and belief in a POSTLIFE.
  
$H_A$ The Alternate Hypothesis is that there is a relationship between the belief in the BIGBANG and belief in a POSTLIFE.
  
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~BIGBANG + POSTLIFE,data=GSS)
barchartGC(~BIGBANG + POSTLIFE,data=GSS, type="percent")

```
  
According to the graph, about 8% of people who do not believe in the BIGBANG theory also do not believe in a POSTLIFE.About 92% of people who do not believe in the BIGBANG theory do believe in a POSTLIFE. We can also see that about 18% who do believe in the BIGBANG theory do not believe in a POSTLIFE and that 82% who believe in the BIGBANG theory do believe in a POSTLIFE.  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
table1 <- xtabs(~BIGBANG + POSTLIFE, data=GSS)
rowPerc(table1)
colPerc(table1)
```
  
 As we can see from the numerical graph, out of 100 individuals who do not believe in the BIGBANG theory about 8% do not believe in a POSTLIFE and about 92% do believe in a POSTLIFE. It is also shown in the second graph that out of 100 who do not believe in a POSTLIFE around 35% do not believe in the BIGBANG theory while 65% do. There appears to be no significant difference.
 
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
  
By taking a look at the Fisher's exam, one can see that the p-value is 0.07143, which is above the 0.05. This indicates that a relationship between the two may be possible.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
  In conclusion, we fail to reject the null hypothesis as there does not seem to be evidence between believing in the BIGBANG and POSTLIFE. 